---
title: "Cleaning ALA data to Final Data"
output:
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: inline
---
Installing packages
```{r}
library(tinytex)
library(dplyr)
```

Reading in data downloaded from Atlas of Living Australia
```{r}
data <- read.csv("ALA data.csv")
```

Filtering data
```{r}
data <- data %>%
  filter(!is.na(Year) & !is.na(Species) & !is.na(Latitude) & !is.na(Longitude)) %>% #excluding data points without a year, species, coordinates
  filter(CoordinateUncertainty <= 50)
```

I added google elevation data to the ALA data (I used a google elevation api to get the elevations from the coordinates as the elevation on ALA is not accurate)
The methods for this analysis is in the Rmarkdown file "Get Google Elevation data.Rmd"

Adding columns for min and max elevation
```{r}
data <- data %>%
            group_by(Species) %>%               #grouping into species
            mutate(minElevation = min(GoogleElevation)) %>%  #adding column for minimum elevation values for each species
            ungroup()

data <- data %>%
            group_by(Species) %>%               # grouping into species
            mutate(maxElevation = max(GoogleElevation)) %>% #adding column for maximum elevation values for each species
  ungroup() 
```

Filtering data to only include data points above 1350m 
```{r}
data <- data %>%
      filter(minElevation>=1350) %>%       # deleting datapoints with min elevation that is <1350m
      ungroup()                            # ungrouping into species
```

finding which species with max range visible below 2200m
```{r}
Hypothesis2Species <- data %>% 
  filter(maxElevation<2200) %>% 
  group_by(Species) %>% 
  summarize(count=n()) %>%
  filter(count >= 20) %>% # returns 1-33 species
  rename(count = count)
```

finding which species with max range not visible below 2200m
```{r} 
Hypothesis3Species <- data %>% 
  filter(maxElevation>2200)%>%
  group_by(Species) %>% 
  summarize(count=n()) %>%
  filter(count >= 20)  %>% # returns 1-23 species
  rename(count = count)
```

Combining hypothesis 2 and 3 species to get a list of all species 
```{r}
AllSpecies <- rbind(Hypothesis2Species, Hypothesis3Species)
```

Generating final data set with 50 coordinate uncertainty and 20 datapoints 
```{r}
FinalData <- list(data, AllSpecies) %>%
  purrr::reduce(left_join, by = "Species") %>%
  filter(count>=20) # filtering data for species with greater than 20 counts
```

creating csv of final data
```{r}
write.csv(FinalData, "Final Data.csv")
```

Combining my Final ALA data with my modern collection data
```{r}
ModernData <- read.csv("Modern Data.csv")
HistoricData <- read.csv("Final Data.csv")

HistoricModernData <- as.data.frame(bind_rows(ModernData, HistoricData))  

write.csv(HistoricModernData, "Historic and Modern Data.csv")
```

