---
title: "Linear moels and graphing final data"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

```{r}
library(ggplot2)
library(dplyr)
library(gridExtra)
library(broom)
library(ggforce)
library(tidyr)
library(ggtext)
```

Read in data created in "Cleaning ALA data to Final Data.Rmd"
```{r}
FinalData <- read.csv("Historic and Modern Data.csv")
```

Species list from Final Data
```{r}
SpeciesList <- FinalData %>% 
  group_by(Species) %>% 
  summarize(count=n())
```

Turning Species List into csv for future metaanalysis for sample size (count)
```{r}
write.csv(SpeciesList, "Species list and count.csv")
```

running single regression without random effect
```{r}
lm.ranun <- FinalData %>%                          
  filter(Species == "Carpha nivicola") %>%
  stats::lm(GoogleElevation~Year,.) #can just change species for each linear model

summary(lm.ranun)
```

running many linear regressions on ALL SPECIES without random effect
```{r}
mylms <- FinalData %>%
  group_by(Species) %>%
    do(model=lm(GoogleElevation ~ Year,.))

mylmcoefs <- as.data.frame(tidy(mylms, model))

##now run a p adjustment , due to multiple hypothesis 

mylmcoefs$Pcorrected <- p.adjust(mylmcoefs$p.value, "holm")

write.csv(mylmcoefs, "Linear Models for all species.csv")
```


```{r}
ListSpecies <- split(FinalData, FinalData$Species)
```

Graphing for a single species, year vs elevation, linear model with random effect for year for each species (with coord cartisian on both axis)
```{r}
#1 Aciphylla glacialis
Aciphylla.glacialis.plot <- ggplot(filter(FinalData, Species =="Aciphylla glacialis")) +
  geom_point(aes(Year, GoogleElevation), colour="darksalmon", size=3.5) + 
  geom_quantile(quantiles = 0.05, size = 2.5, aes(Year, GoogleElevation), linetype = "longdash",  colour="darkolivegreen3") +
  labs(title="*Aciphylla glacialis*", x="", y="") +
  theme_bw() +
  theme(plot.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  theme(panel.border= element_blank()) +
  theme(plot.title = element_markdown(hjust = 0.5, size=28)) +  
  theme(axis.line = element_line(color="black", size = 0.5)) +
  theme(axis.text.x = element_blank()) +
  theme(axis.text.y = element_text(size=22)) +
  coord_cartesian(xlim = c(1965, 2020), ylim = c(1350, 2230)) 

#2 Agrostis muelleriana
Agrostis.muelleriana.plot <- ggplot(filter(FinalData, Species =="Agrostis muelleriana")) +
  geom_point(aes(Year, GoogleElevation), colour="darksalmon", size=3.5) + 
  labs(title="*Agrostis muelleriana*", x="", y="") +
  geom_quantile(quantiles = 0.05, size = 2.5, aes(Year, GoogleElevation), linetype = "longdash",  colour="darkolivegreen3") +
  theme_bw() +
  theme(plot.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  theme(panel.border= element_blank()) +
  theme(plot.title = element_markdown(hjust = 0.5, size=28)) +  
  theme(axis.line = element_line(color="black", size = 0.5)) +
  theme(axis.text = element_blank()) +
  coord_cartesian(xlim = c(1965, 2020), ylim = c(1350, 2230))


#3 Astelia alpina
Astelia.alpina.plot <- ggplot(filter(FinalData, Species =="Astelia alpina var. novae-hollandiae ")) +
  geom_point(aes(Year, GoogleElevation), colour="darksalmon", size=3.5) + 
  labs(title= "*Astelia alpina* var. *novae-hollandiae*", x="", y="") +
  geom_quantile(quantiles = 0.05, size = 2.5, aes(Year, GoogleElevation), linetype = "solid",  colour="darkolivegreen3") +
  geom_quantile(quantiles = 0.95, size = 2.5, aes(Year, GoogleElevation), linetype = "solid",  colour="darkolivegreen3") +
  theme_bw() +
  theme(plot.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  theme(panel.border= element_blank()) +
  theme(plot.title = element_markdown(hjust = 0.5, size=28)) + 
  theme(axis.line = element_line(color="black", size = 0.5)) +
  theme(axis.text = element_text(size=22)) +
  theme(axis.text.x = element_blank()) +
  geom_smooth(aes(Year, GoogleElevation), method="lm", se=FALSE, colour="skyblue2", fill="skyblue2", alpha=.15, size= 2.5) +
  coord_cartesian(xlim = c(1965, 2020), ylim = c(1350, 2230)) 

#4 Astelia psychrocharis
Astelia.psychrocharis.plot <- ggplot(filter(FinalData, Species =="Astelia psychrocharis")) +
  geom_point(aes(Year, GoogleElevation), colour="darksalmon", size=3.5) + 
  labs(title="*Astelia psychrocharis*", x="", y="") +
  geom_quantile(quantiles = 0.05, size = 2.5, aes(Year, GoogleElevation), linetype = "solid",  colour="darkolivegreen3") +
  geom_quantile(quantiles = 0.95, size = 2.5, aes(Year, GoogleElevation), linetype = "solid",  colour="darkolivegreen3") +
  theme_bw() +
  theme(plot.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  theme(panel.border= element_blank()) +
  theme(plot.title = element_markdown(hjust = 0.5, size=28)) +  
  theme(axis.line = element_line(color="black", size = 0.5)) +
  theme(axis.text = element_blank()) +
  geom_smooth(aes(Year, GoogleElevation), method="lm", se=FALSE, colour="skyblue2", fill="skyblue2", alpha=.15, size= 2.5) +
  coord_cartesian(xlim = c(1965, 2020), ylim = c(1350, 2230))

#5 Brachyscome stolonifera
Brachyscome.stolonifera.plot <- ggplot(filter(FinalData, Species =="Brachyscome stolonifera")) +
  geom_point(aes(Year, GoogleElevation), colour="darksalmon", size=3.5) + 
  labs(title="*Brachyscome stolonifera*", x="", y="") +
  geom_quantile(quantiles = 0.05, size = 2.5, aes(Year, GoogleElevation), linetype = "solid",  colour="darkolivegreen3") +
  geom_quantile(quantiles = 0.95, size = 2.5, aes(Year, GoogleElevation), linetype = "longdash",  colour="darkolivegreen3") +
  theme_bw() +
  theme(plot.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  theme(panel.border= element_blank()) +
  theme(plot.title = element_markdown(hjust = 0.5, size=28)) +  
  theme(axis.line = element_line(color="black", size = 0.5)) +
  theme(axis.text = element_blank()) +
   geom_smooth(aes(Year, GoogleElevation), method="lm", se=FALSE, colour="skyblue2", fill="skyblue2", alpha=.15, size= 2.5) +
  coord_cartesian(xlim = c(1965, 2020), ylim = c(1350, 2230))


#8	Carex echinata
Carex.echinata.plot <- ggplot(filter(FinalData, Species =="Carex echinata")) +
  geom_point(aes(Year, GoogleElevation), colour="darksalmon", size=3.5) + 
  labs(title="*Carex echinata*", x="", y="") +
  geom_quantile(quantiles = 0.05, size = 2.5, aes(Year, GoogleElevation), linetype = "longdash",  colour="darkolivegreen3") +
  geom_quantile(quantiles = 0.95, size = 2.5, aes(Year, GoogleElevation), linetype = "longdash",  colour="darkolivegreen3") +
  theme_bw() +
  theme(plot.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  theme(panel.border= element_blank()) +
  theme(plot.title = element_markdown(hjust = 0.5, size=28)) +  
  theme(axis.line = element_line(color="black", size = 0.5)) +
  theme(axis.text.x = element_blank()) +
  theme(axis.text.y = element_text(size=22)) +
  coord_cartesian(xlim = c(1965, 2020), ylim = c(1350, 2230))

#9	Carex hypandra
Carex.hypandra.plot <- ggplot(filter(FinalData, Species =="Carex hypandra")) +
  geom_point(aes(Year, GoogleElevation), colour="darksalmon", size=3.5) + 
  labs(title="*Carex hypandra*", x="", y="") +
  geom_quantile(quantiles = 0.05, size = 2.5, aes(Year, GoogleElevation), linetype = "solid",  colour="darkolivegreen3") +
  geom_quantile(quantiles = 0.95, size = 2.5, aes(Year, GoogleElevation), linetype = "longdash",  colour="darkolivegreen3") +
  theme_bw() +
  theme(plot.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  theme(panel.border= element_blank()) +
  theme(plot.title = element_markdown(hjust = 0.5, size=28)) +  
  theme(axis.line = element_line(color="black", size = 0.5)) +
  theme(axis.text = element_blank()) +
  geom_smooth(aes(Year, GoogleElevation), method="lm", se=FALSE, colour="skyblue2", fill="skyblue2", alpha=.15, size= 2.5) +
  coord_cartesian(xlim = c(1965, 2020), ylim = c(1350, 2230))

#10	Carex pyrenaica var. cephalotes
Carex.pyrenaica.plot <- ggplot(filter(FinalData, Species =="Carex pyrenaica var. cephalotes")) +
  geom_point(aes(Year, GoogleElevation), colour="darksalmon", size=3.5) + 
  labs(title="*Carex pyrenaica* var. *cephalotes*", x="", y="") +
  geom_quantile(quantiles = 0.05, size = 2.5, aes(Year, GoogleElevation), linetype = "longdash",  colour="darkolivegreen3") +
  theme_bw() +
  theme(plot.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  theme(panel.border= element_blank()) +
  theme(plot.title = element_markdown(hjust = 0.5, size=28)) +  
  theme(axis.line = element_line(color="black", size = 0.5)) +
  theme(axis.text = element_blank()) +
  geom_smooth(aes(Year, GoogleElevation), method="lm", se=FALSE, colour="skyblue2", fill="skyblue2", alpha=.15, size= 2.5) +
  coord_cartesian(xlim = c(1965, 2020), ylim = c(1350, 2230))

#11	Carpha alpina
Carpha.alpina.plot <- ggplot(filter(FinalData, Species =="Carpha alpina")) +
  geom_point(aes(Year, GoogleElevation), colour="darksalmon", size=3.5) + 
  geom_quantile(quantiles = 0.05, size = 2.5, aes(Year, GoogleElevation), linetype = "longdash",  colour="darkolivegreen3") +
  geom_quantile(quantiles = 0.95, size = 2.5, aes(Year, GoogleElevation), linetype = "solid",  colour="darkolivegreen3") +
  labs(title="*Carpha alpina*", x="", y="") +
  theme_bw() +
  theme(plot.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  theme(panel.border= element_blank()) +
  theme(plot.title = element_markdown(hjust = 0.5, size=28)) +  
  theme(axis.line = element_line(color="black", size = 0.5)) +
  theme(axis.text = element_blank()) +
  coord_cartesian(xlim = c(1965, 2020), ylim = c(1350, 2230))

#12	Carpha nivicola
Carpha.nivicola.plot <- ggplot(filter(FinalData, Species =="Carpha nivicola")) +
  geom_point(aes(Year, GoogleElevation), colour="darksalmon", size=3.5) + 
  labs(title="*Carpha nivicola*", x="", y="") +
  geom_quantile(quantiles = 0.05, size = 2.5, aes(Year, GoogleElevation), linetype = "longdash",  colour="darkolivegreen3") +
  geom_quantile(quantiles = 0.95, size = 2.5, aes(Year, GoogleElevation), linetype = "longdash",  colour="darkolivegreen3") +
  theme_bw() +
  theme(plot.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  theme(panel.border= element_blank()) +
  theme(plot.title = element_markdown(hjust = 0.5, size=28)) +  
  theme(axis.line = element_line(color="black", size = 0.5)) +
  theme(axis.text.x = element_blank()) +
  theme(axis.text.y = element_text(size=22)) +
  coord_cartesian(xlim = c(1965, 2020), ylim = c(1350, 2230))

#13 Chionochloa frigida
Chionochloa.frigida.plot <- ggplot(filter(FinalData, Species =="Chionochloa frigida")) +
  geom_point(aes(Year, GoogleElevation), colour="darksalmon", size=3.5) + 
  labs(title="*Chionochloa frigida*", x="", y="") +
  geom_quantile(quantiles = 0.05, size = 2.5, aes(Year, GoogleElevation), linetype = "solid",  colour="darkolivegreen3") +
  geom_quantile(quantiles = 0.95, size = 2.5, aes(Year, GoogleElevation), linetype = "longdash",  colour="darkolivegreen3") +
  theme_bw() +
  theme(plot.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  theme(panel.border= element_blank()) +
  theme(plot.title = element_markdown(hjust = 0.5, size=28)) +  
  theme(axis.line = element_line(color="black", size = 0.5)) +
  theme(axis.text = element_blank()) +
  geom_smooth(aes(Year, GoogleElevation), method="lm", se=FALSE, colour="skyblue2", fill="skyblue2", alpha=.15, size= 2.5) +
  coord_cartesian(xlim = c(1965, 2020), ylim = c(1350, 2230))

#14	Colobanthus affinis
Colobanthus.affinis.plot <- ggplot(filter(FinalData, Species =="Colobanthus affinis")) +
  geom_point(aes(Year, GoogleElevation), colour="darksalmon", size=3.5) + 
  labs(title="*Colobanthus affinis*", x="", y="") +
  geom_quantile(quantiles = 0.05, size = 2.5, aes(Year, GoogleElevation), linetype = "solid",  colour="darkolivegreen3") +
  theme_bw() +
  theme(plot.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  theme(panel.border= element_blank()) +
  theme(plot.title = element_markdown(hjust = 0.5, size=28)) +  
  theme(axis.line = element_line(color="black", size = 0.5)) +
  theme(axis.text.x = element_blank()) +
  theme(axis.text.y = element_text(size=22)) +
  geom_smooth(aes(Year, GoogleElevation), method="lm", se=FALSE, colour="skyblue2", fill="skyblue2", alpha=.15, size= 2.5) +
  coord_cartesian(xlim = c(1965, 2020), ylim = c(1350, 2230))



#20	Dichosciadium ranunculaceum
Dichosciadium.ranunculaceum.plot <- ggplot(filter(FinalData, Species =="Dichosciadium ranunculaceum var. ranunculaceum")) +
  geom_point(aes(Year, GoogleElevation), colour="darksalmon", size=3.5) + 
  labs(title="*Dichosciadium ranunculaceum* var. *ranunculaceum*", x="", y="") +
  geom_quantile(quantiles = 0.05, size = 2.5, aes(Year, GoogleElevation), linetype = "longdash",  colour="darkolivegreen3") +
  theme_bw() +
  theme(plot.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  theme(panel.border= element_blank()) +
  theme(plot.title = element_markdown(hjust = 0.5, size=28)) +  
  theme(axis.line = element_line(color="black", size = 0.5)) +
  theme(axis.text = element_blank()) +
  geom_smooth(aes(Year, GoogleElevation), method="lm", se=FALSE, colour="skyblue2", fill="skyblue2", alpha=.15, size= 2.5) +
  coord_cartesian(xlim = c(1965, 2020), ylim = c(1350, 2230))

#21	Drosera arcturi
Drosera.arcturi.plot <- ggplot(filter(FinalData, Species =="Drosera arcturi")) +
  geom_point(aes(Year, GoogleElevation), colour="darksalmon", size=3.5) + 
  geom_quantile(quantiles = 0.05, size = 2.5, aes(Year, GoogleElevation), linetype = "longdash",  colour="darkolivegreen3") +
  labs(title="*Drosera arcturi*", x="", y="") +
  theme_bw() +
  theme(plot.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  theme(panel.border= element_blank()) +
  theme(plot.title = element_markdown(hjust = 0.5, size=28)) +  
  theme(axis.line = element_line(color="black", size = 0.5)) +
  theme(axis.text = element_blank())+
  coord_cartesian(xlim = c(1965, 2020), ylim = c(1350, 2230))

#22	Epacris glacialis
Epacris.glacialis.plot <- ggplot(filter(FinalData, Species =="Epacris glacialis")) +
  geom_point(aes(Year, GoogleElevation), colour="darksalmon", size=3.5) + 
  labs(title="*Epacris glacialis*", x="", y="") +
  geom_quantile(quantiles = 0.05, size = 2.5, aes(Year, GoogleElevation), linetype = "longdash",  colour="darkolivegreen3") +
  theme_bw() +
  theme(plot.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  theme(panel.border= element_blank()) +
  theme(plot.title = element_markdown(hjust = 0.5, size=28)) +  
  theme(axis.line = element_line(color="black", size = 0.5)) +
  theme(axis.text.x = element_blank()) +
  theme(axis.text.y = element_text(size=22)) +
  coord_cartesian(xlim = c(1965, 2020), ylim = c(1350, 2230))


#24	Ewartia nubigena
Ewartia.nubigena.plot <- ggplot(filter(FinalData, Species =="Ewartia nubigena")) +
  geom_point(aes(Year, GoogleElevation), colour="darksalmon", size=3.5) + 
  labs(title="*Ewartia nubigena*", x="", y="") +
  geom_quantile(quantiles = 0.05, size = 2.5, aes(Year, GoogleElevation), linetype = "longdash",  colour="darkolivegreen3") +
  theme_bw() +
  theme(plot.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  theme(panel.border= element_blank()) +
  theme(plot.title = element_markdown(hjust = 0.5, size=28)) +  
  theme(axis.line = element_line(color="black", size = 0.5)) +
  theme(axis.text = element_blank()) +
  coord_cartesian(xlim = c(1965, 2020), ylim = c(1350, 2230))


#26	Luzula acutifolia
Luzula.acutifolia.plot <- ggplot(filter(FinalData, Species =="Luzula acutifolia subsp. nana")) +
  geom_point(aes(Year, GoogleElevation), colour="darksalmon", size=3.5) + 
  labs(title= "*Luzula acutifolia* subsp. *nana*", x="", y="") +
  geom_quantile(quantiles = 0.05, size = 2.5, aes(Year, GoogleElevation), linetype = "solid",  colour="darkolivegreen3") +
  theme_bw() +
  theme(plot.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  theme(panel.border= element_blank()) +
  theme(plot.title = element_markdown(hjust = 0.5, size=28)) +  
  theme(axis.line = element_line(color="black", size = 0.5)) +
  theme(axis.text = element_blank()) +
  geom_smooth(aes(Year, GoogleElevation), method="lm", se=FALSE, colour="skyblue2", fill="skyblue2", alpha=.15, size= 2.5) +
  coord_cartesian(xlim = c(1965, 2020), ylim = c(1350, 2230))


#28	Luzula australasica
Luzula.australasica.plot <- ggplot(filter(FinalData, Species =="Luzula australasica subsp. dura")) +
  geom_point(aes(Year, GoogleElevation), colour="darksalmon", size=3.5) + 
  labs(title="*Luzula australasica* subsp. *dura*", x="", y="") +
  geom_quantile(quantiles = 0.05, size = 2.5, aes(Year, GoogleElevation), linetype = "longdash",  colour="darkolivegreen3") +
  theme_bw() +
  theme(plot.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  theme(panel.border= element_blank()) +
  theme(plot.title = element_markdown(hjust = 0.5, size=28)) +  
  theme(axis.line = element_line(color="black", size = 0.5)) +
  theme(axis.text.x = element_blank()) +
  theme(axis.text.y = element_text(size=22))
  coord_cartesian(xlim = c(1965, 2020), ylim = c(1350, 2230))

#29	Lycopodium fastigiatum
Lycopodium.fastigiatum.plot <- ggplot(filter(FinalData, Species =="Lycopodium fastigiatum")) +
  geom_point(aes(Year, GoogleElevation), colour="darksalmon", size=3.5) + 
  labs(title="*Lycopodium fastigiatum*", x="", y="") +
  geom_quantile(quantiles = 0.05, size = 2.5, aes(Year, GoogleElevation), linetype = "longdash",  colour="darkolivegreen3") +
  theme_bw() +
  theme(plot.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  theme(panel.border= element_blank()) +
  theme(plot.title = element_markdown(hjust = 0.5, size=28)) +  
  theme(axis.line = element_line(color="black", size = 0.5)) +
  theme(axis.text = element_blank()) +
  geom_smooth(aes(Year, GoogleElevation), method="lm", se=FALSE, colour="skyblue2", fill="skyblue2", alpha=.15, size= 2.5) +
   geom_smooth(aes(Year, GoogleElevation), method="lm", se=FALSE, colour="skyblue2", fill="skyblue2", alpha=.15, size= 2.5) +
  coord_cartesian(xlim = c(1965, 2020), ylim = c(1350, 2230))

#30	Nematolepis ovatifolia
Nematolepis.ovatifolia.plot <- ggplot(filter(FinalData, Species =="Nematolepis ovatifolia")) +
  geom_point(aes(Year, GoogleElevation), colour="darksalmon", size=3.5) + 
  labs(title="*Nematolepis ovatifolia*", x="", y="") +
  geom_quantile(quantiles = 0.05, size = 2.5, aes(Year, GoogleElevation), linetype = "longdash",  colour="darkolivegreen3") +
  theme_bw() +
  theme(plot.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  theme(panel.border= element_blank()) +
  theme(plot.title = element_markdown(hjust = 0.5, size=28)) +  
  theme(axis.line = element_line(color="black", size = 0.5)) +
  theme(axis.text = element_blank()) +
  coord_cartesian(xlim = c(1965, 2020), ylim = c(1350, 2230))

#31	Oreobolus pumilio
Oreobolus.pumilio.plot <- ggplot(filter(FinalData, Species =="Oreobolus pumilio")) +
  geom_point(aes(Year, GoogleElevation), colour="darksalmon", size=3.5) + 
  labs(title="*Oreobolus pumilio*", x="", y="") +
  geom_quantile(quantiles = 0.05, size = 2.5, aes(Year, GoogleElevation), linetype = "longdash",  colour="darkolivegreen3") +
  geom_quantile(quantiles = 0.95, size = 2.5, aes(Year, GoogleElevation), linetype = "longdash",  colour="darkolivegreen3") +
  theme_bw() +
  theme(plot.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  theme(panel.border= element_blank()) +
  theme(plot.title = element_markdown(hjust = 0.5, size=28)) +  
  theme(axis.line = element_line(color="black", size = 0.5)) +
  theme(axis.text = element_blank()) +
  coord_cartesian(xlim = c(1965, 2020), ylim = c(1350, 2230))

#32	Oreomyrrhis brevipes
Oreomyrrhis.brevipes.plot <- ggplot(filter(FinalData, Species =="Oreomyrrhis brevipes")) +
  geom_point(aes(Year, GoogleElevation), colour="darksalmon", size=3.5) + 
  labs(title="*Oreomyrrhis brevipes*", x="", y="") +
  geom_quantile(quantiles = 0.05, size = 2.5, aes(Year, GoogleElevation), linetype = "longdash",  colour="darkolivegreen3") +
  geom_quantile(quantiles = 0.95, size = 2.5, aes(Year, GoogleElevation), linetype = "longdash",  colour="darkolivegreen3") +
  theme_bw() +
  theme(plot.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  theme(panel.border= element_blank()) +
  theme(plot.title = element_markdown(hjust = 0.5, size=28)) +  
  theme(axis.line = element_line(color="black", size = 0.5)) +
  theme(axis.text.x = element_blank()) +
  theme(axis.text.y = element_text(size=22)) +
  coord_cartesian(xlim = c(1965, 2020), ylim = c(1350, 2230))

#33	Oreomyrrhis pulvinifica
Oreomyrrhis.pulvinifica.plot <- ggplot(filter(FinalData, Species =="Oreomyrrhis pulvinifica")) +
  geom_point(aes(Year, GoogleElevation), colour="darksalmon", size=3.5) + 
  labs(title="*Oreomyrrhis pulvinifica*", x="", y="") +
  geom_quantile(quantiles = 0.05, size = 2.5, aes(Year, GoogleElevation), linetype = "longdash",  colour="darkolivegreen3") +
  theme_bw() +
  theme(plot.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  theme(panel.border= element_blank()) +
  theme(plot.title = element_markdown(hjust = 0.5, size=28)) +  
  theme(axis.line = element_line(color="black", size = 0.5)) +
  theme(axis.text.x = element_blank()) +
  theme(axis.text.y = element_text(size=22)) +
  coord_cartesian(xlim = c(1965, 2020), ylim = c(1350, 2230))

#34	Orites lancifolius
Orites.lancifolius.plot <- ggplot(filter(FinalData, Species =="Orites lancifolius")) +
  geom_point(aes(Year, GoogleElevation), colour="darksalmon", size=3.5) + 
  labs(title="*Orites lancifolius*", x="", y="") +
  geom_quantile(quantiles = 0.05, size = 2.5, aes(Year, GoogleElevation), linetype = "longdash",  colour="darkolivegreen3") +
  geom_quantile(quantiles = 0.95, size = 2.5, aes(Year, GoogleElevation), linetype = "solid",  colour="darkolivegreen3") +
  theme_bw() +
  theme(plot.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  theme(panel.border= element_blank()) +
  theme(plot.title = element_markdown(hjust = 0.5, size=28)) +  
  theme(axis.line = element_line(color="black", size = 0.5)) +
  theme(axis.text = element_blank()) +
  coord_cartesian(xlim = c(1965, 2020), ylim = c(1350, 2230))

#35	Ozothamnus alpinus
Ozothamnus.alpinus.plot <- ggplot(filter(FinalData, Species =="Ozothamnus alpinus")) +
  geom_point(aes(Year, GoogleElevation), colour="darksalmon", size=3.5) + 
  geom_quantile(quantiles = 0.05, size = 2.5, aes(Year, GoogleElevation), linetype = "longdash",  colour="darkolivegreen3") +
  geom_quantile(quantiles = 0.95, size = 2.5, aes(Year, GoogleElevation), linetype = "longdash",  colour="darkolivegreen3") +
  labs(title="*Ozothamnus alpinus*", x="", y="") +
  theme_bw() +
  theme(plot.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  theme(panel.border= element_blank()) +
  theme(plot.title = element_markdown(hjust = 0.5, size=28)) +  
  theme(axis.line = element_line(color="black", size = 0.5)) +
  theme(axis.text = element_blank()) +
  coord_cartesian(xlim = c(1965, 2020), ylim = c(1350, 2230))

#37	Pappochroma setosum
Pappochroma.setosum.plot <- ggplot(filter(FinalData, Species =="Pappochroma setosum")) +
  geom_point(aes(Year, GoogleElevation), colour="darksalmon", size=3.5) + 
  labs(title="*Pappochroma setosum*", x="", y="") +
  geom_quantile(quantiles = 0.05, size = 2.5, aes(Year, GoogleElevation), linetype = "solid",  colour="darkolivegreen3") +
  geom_quantile(quantiles = 0.95, size = 2.5, aes(Year, GoogleElevation), linetype = "longdash",  colour="darkolivegreen3") +
  theme_bw() +
  theme(plot.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  theme(panel.border= element_blank()) +
  theme(plot.title = element_markdown(hjust = 0.5, size=28)) +  
  theme(axis.line = element_line(color="black", size = 0.5)) +
  theme(axis.text.x = element_blank()) +
  theme(axis.text.y = element_text(size=22)) +
  geom_smooth(aes(Year, GoogleElevation), method="lm", se=FALSE, colour="skyblue2", fill="skyblue2", alpha=.15, size= 2.5) +
  coord_cartesian(xlim = c(1965, 2020), ylim = c(1350, 2230))


#39	Pentachondra pumila
Pentachondra.pumila.plot <- ggplot(filter(FinalData, Species =="Pentachondra pumila")) +
  geom_point(aes(Year, GoogleElevation), colour="darksalmon", size=3.5) + 
  labs(title="*Pentachondra pumila*", x="", y="") +
  geom_quantile(quantiles = 0.05, size = 2.5, aes(Year, GoogleElevation), linetype = "solid",  colour="darkolivegreen3") +
  theme_bw() +
  theme(plot.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  theme(panel.border= element_blank()) +
  theme(plot.title = element_markdown(hjust = 0.5, size=28)) +  
  theme(axis.line = element_line(color="black", size = 0.5)) +
  theme(axis.text = element_blank()) +
  geom_smooth(aes(Year, GoogleElevation), method="lm", se=FALSE, colour="skyblue2", fill="skyblue2", alpha=.15, size= 2.5) +
  coord_cartesian(xlim = c(1965, 2020), ylim = c(1350, 2230))

#40	Plantago glacialis
Plantago.glacialis.plot <- ggplot(filter(FinalData, Species == "Plantago glacialis")) +
  geom_point(aes(Year, GoogleElevation), colour="darksalmon", size=3.5) + 
  geom_quantile(quantiles = 0.05, size = 2.5, aes(Year, GoogleElevation), linetype = "longdash",  colour="darkolivegreen3") +
  geom_quantile(quantiles = 0.95, size = 2.5, aes(Year, GoogleElevation), linetype = "longdash",  colour="darkolivegreen3") +
  labs(title="*Plantago glacialis*", x="", y="") +
  theme_bw() +
  theme(plot.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  theme(panel.border= element_blank()) +
  theme(plot.title = element_markdown(hjust = 0.5, size=28)) +  
  theme(axis.line = element_line(color="black", size = 0.5)) +
  theme(axis.text = element_blank()) +
  coord_cartesian(xlim = c(1965, 2020), ylim = c(1350, 2230))


#44	Prasophyllum tadgellianum
Prasophyllum.tadgellianum.plot <- ggplot(filter(FinalData, Species == "Prasophyllum tadgellianum")) +
  geom_point(aes(Year, GoogleElevation), colour="darksalmon", size=3.5) + 
  geom_quantile(quantiles = 0.05, size = 2.5, aes(Year, GoogleElevation), linetype = "longdash",  colour="darkolivegreen3") +
  labs(title="*Prasophyllum tadgellianum*", x="", y="") +
  theme_bw() +
  theme(plot.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  theme(panel.border= element_blank()) +
  theme(plot.title = element_markdown(hjust = 0.5, size=28)) +  
  theme(axis.line = element_line(color="black", size = 0.5)) +
  theme(axis.text = element_blank()) +
  coord_cartesian(xlim = c(1965, 2020), ylim = c(1350, 2230))

#45	Psychrophila introloba
Psychrophila.introloba.plot <- ggplot(filter(FinalData, Species == "Psychrophila introloba")) +
  geom_point(aes(Year, GoogleElevation), colour="darksalmon", size=3.5) + 
  labs(title="*Psychrophila introloba*", x="", y="") +
  geom_quantile(quantiles = 0.05, size = 2.5, aes(Year, GoogleElevation), linetype = "solid",  colour="darkolivegreen3") +
  theme_bw() +
  theme(plot.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  theme(panel.border= element_blank()) +
  theme(plot.title = element_markdown(hjust = 0.5, size=28)) +  
  theme(axis.line = element_line(color="black", size = 0.5)) +
  theme(axis.text = element_text(size = 22)) +
 geom_smooth(aes(Year, GoogleElevation), method="lm", se=FALSE, colour="skyblue2", fill="skyblue2", alpha=.15, size= 2.5) +
  coord_cartesian(xlim = c(1965, 2020), ylim = c(1350, 2230))

#46	Ranunculus anemoneus
Ranunculus.anemoneus.plot <- ggplot(filter(FinalData, Species == "Ranunculus anemoneus")) +
  geom_point(aes(Year, GoogleElevation), colour="darksalmon", size=3.5) + 
  labs(title="*Ranunculus anemoneus*", x="", y="") +
  geom_quantile(quantiles = 0.05, size = 2.5, aes(Year, GoogleElevation), linetype = "longdash",  colour="darkolivegreen3") +
  theme_bw() +
  theme(plot.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  theme(panel.border= element_blank()) +
  theme(plot.title = element_markdown(hjust = 0.5, size=28)) +  
  theme(axis.line = element_line(color="black", size = 0.5)) +
  theme(axis.text.y = element_blank()) +
  theme(axis.text.x = element_text(size=22)) +
  geom_smooth(aes(Year, GoogleElevation), method="lm", se=FALSE, colour="skyblue2", fill="skyblue2", alpha=.15, size= 2.5) +
  coord_cartesian(xlim = c(1965, 2020), ylim = c(1350, 2230))


#50	Ranunculus muelleri
Ranunculus.muelleri.plot <- ggplot(filter(FinalData, Species == "Ranunculus muelleri")) +
  geom_point(aes(Year, GoogleElevation), colour="darksalmon", size=3.5) + 
  labs(title="*Ranunculus muelleri*", x="", y="") +
  geom_quantile(quantiles = 0.05, size = 2.5, aes(Year, GoogleElevation), linetype = "longdash",  colour="darkolivegreen3") +
  geom_quantile(quantiles = 0.95, size = 2.5, aes(Year, GoogleElevation), linetype = "solid",  colour="darkolivegreen3") +
  theme_bw() +
  theme(plot.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  theme(panel.border= element_blank()) +
  theme(plot.title = element_markdown(hjust = 0.5, size=28)) +  
  theme(axis.line = element_line(color="black", size = 0.5)) +
  theme(axis.text = element_blank()) +
  coord_cartesian(xlim = c(1965, 2020), ylim = c(1350, 2230))

#51	Ranunculus niphophilus
Ranunculus.niphophilus.plot <- ggplot(filter(FinalData, Species == "Ranunculus niphophilus")) +
  geom_point(aes(Year, GoogleElevation), colour="darksalmon", size=3.5) + 
  geom_quantile(quantiles = 0.05, size = 2.5, aes(Year, GoogleElevation), linetype = "longdash",  colour="darkolivegreen3") +
  geom_quantile(quantiles = 0.95, size = 2.5, aes(Year, GoogleElevation), linetype = "longdash",  colour="darkolivegreen3") +
  labs(title="*Ranunculus niphophilus*", x="", y="") +
  theme_bw() +
  theme(plot.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  theme(panel.border= element_blank()) +
  theme(plot.title = element_markdown(hjust = 0.5, size=28)) +  
  theme(axis.line = element_line(color="black", size = 0.5)) +
  theme(axis.text = element_text(size=22)) +
  coord_cartesian(xlim = c(1965, 2020), ylim = c(1350, 2230))

#52	Rytidosperma alpicola
Rytidosperma.alpicola.plot <- ggplot(filter(FinalData, Species == "Rytidosperma alpicola")) +
  geom_point(aes(Year, GoogleElevation), colour="darksalmon", size=3.5) + 
  labs(title="*Rytidosperma alpicola*", x="", y="") +
  geom_quantile(quantiles = 0.05, size = 2.5, aes(Year, GoogleElevation), linetype = "longdash",  colour="darkolivegreen3") +
  geom_quantile(quantiles = 0.95, size = 2.5, aes(Year, GoogleElevation), linetype = "longdash",  colour="darkolivegreen3") +
  theme_bw() +
  theme(plot.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  theme(panel.border= element_blank()) +
  theme(plot.title = element_markdown(hjust = 0.5, size=28)) +  
  theme(axis.line = element_line(color="black", size = 0.5)) +
  theme(axis.text.x = element_text(size=22)) +
  theme(axis.text.y = element_blank()) +
  coord_cartesian(xlim = c(1965, 2020), ylim = c(1350, 2230))


#55	Senecio pectinatus
Senecio.pectinatus.plot <- ggplot(filter(FinalData, Species == "Senecio pectinatus var. major")) +
  geom_point(aes(Year, GoogleElevation), colour="darksalmon", size=3.5) + 
  labs(title="*Senecio pectinatus* var. *major*", x="", y="") +
  geom_quantile(quantiles = 0.05, size = 2.5, aes(Year, GoogleElevation), linetype = "longdash",  colour="darkolivegreen3") +
  geom_quantile(quantiles = 0.95, size = 2.5, aes(Year, GoogleElevation), linetype = "longdash",  colour="darkolivegreen3") +
  theme_bw() +
  theme(plot.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  theme(panel.border= element_blank()) +
  theme(plot.title = element_markdown(hjust = 0.5, size=28)) +  
  theme(axis.line = element_line(color="black", size = 0.5)) +
   theme(axis.text.x = element_text(size=22)) +
  theme(axis.text.y = element_blank()) +
  coord_cartesian(xlim = c(1965, 2020), ylim = c(1350, 2230))

#56	Stackhousia pulvinaris
Stackhousia.pulvinaris.plot <- ggplot(filter(FinalData, Species == "Stackhousia pulvinaris")) +
  geom_point(aes(Year, GoogleElevation), colour="darksalmon", size=3.5) + 
  labs(title="*Stackhousia pulvinaris*", x="", y="") +
  geom_quantile(quantiles = 0.05, size = 2.5, aes(Year, GoogleElevation), linetype = "solid",  colour="darkolivegreen3") +
  theme_bw() +
  theme(plot.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  theme(panel.border= element_blank()) +
  theme(plot.title = element_markdown(hjust = 0.5, size=28)) +  
  theme(axis.line = element_line(color="black", size = 0.5)) +
  theme(axis.text.y = element_blank()) +
  theme(axis.text.x = element_text(size=22)) +
  geom_smooth(aes(Year, GoogleElevation), method="lm", se=FALSE, colour="skyblue2", fill="skyblue2", alpha=.15, size= 2.5) +
  coord_cartesian(xlim = c(1965, 2020), ylim = c(1350, 2230))
```



plotting all plots into a grid 
```{r} 
H2Plots <- grid.arrange(Astelia.alpina.plot, Astelia.psychrocharis.plot, Brachyscome.stolonifera.plot, Carex.echinata.plot, Carex.hypandra.plot, Carpha.alpina.plot, Carpha.nivicola.plot, Chionochloa.frigida.plot, Oreobolus.pumilio.plot, Oreomyrrhis.brevipes.plot, Orites.lancifolius.plot, Ozothamnus.alpinus.plot, Pappochroma.setosum.plot, Plantago.glacialis.plot, Ranunculus.muelleri.plot, Ranunculus.niphophilus.plot, Rytidosperma.alpicola.plot, Senecio.pectinatus.plot, ncol=3)


H3Plots <- grid.arrange(Aciphylla.glacialis.plot, Agrostis.muelleriana.plot, Carex.pyrenaica.plot, Colobanthus.affinis.plot, Dichosciadium.ranunculaceum.plot, Drosera.arcturi.plot, Epacris.glacialis.plot, Ewartia.nubigena.plot, Luzula.acutifolia.plot, Luzula.australasica.plot, Lycopodium.fastigiatum.plot, Nematolepis.ovatifolia.plot, Oreomyrrhis.pulvinifica.plot, Pentachondra.pumila.plot, Prasophyllum.tadgellianum.plot, Psychrophila.introloba.plot, Ranunculus.anemoneus.plot, Stackhousia.pulvinaris.plot, ncol=3)
                      
```

```{r}

ggsave("Hypothesis2 plots.tiff",
       plot= H2Plots, 
       device = "tiff",
       width = 23,
       height = 30,
       dpi = 100)

ggsave("Hypothesis3 plots.tiff",
       plot= H3Plots, 
       device = "tiff",
       width = 23,
       height = 30,
       dpi = 100)
```


